Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-04-13 fib2.tex
fixed minor typo and highlighted a sentence for Simon to fix.

Our concrete simulation proceeds by associating a \emph{tile} with each site of the 
$L\times L$ periodic square lattice. In order to keep track of the observables of the system 
we maintain a set of disjoint curves, representing the history of anyons on the lattice (these 
curves can also be thought of as a top-down view of the fusion tree). The ends of curves 
correspond to leaves of the fusion tree, or anyons. In general, the curves wind around the two 
dimensional tiles in a haphazard way determined by the progress of the simulation. This 
allows a dynamically generated basis for the fusion space that easily allows for tensor 
decomposition into factors corresponding disjoint clusters. For comparison, previous work 
used a single fixed basis for the fusion space (determined by row-major ordering of 
sites)~\cite{Brell2013}.

>>>>

Our concrete simulation proceeds by associating a \emph{tile} with each site of the 
$L\times L$ periodic square lattice. In order to keep track of the observables of the system 
we maintain a set of disjoint curves, representing the history of anyons on the lattice (these 
curves can also be thought of as a top-down view of the fusion tree). 
\stf{this next sentence is currently incorrect.}
The ends of curves 
correspond to leaves of the fusion tree, or anyons. In general, the curves wind around the two 
dimensional tiles in a haphazard way determined by the progress of the simulation. This 
allows a dynamically generated basis for the fusion space that easily allows for tensor 
decomposition into factors corresponding to disjoint clusters. For comparison, previous work 
used a single fixed basis for the fusion space (determined by row-major ordering of 
sites)~\cite{Brell2013}.
